Counterfactual Training

### 2024-12-18 paper/presenations/slides.qmd
come on

- Trying to distribute: 
    1. Models/experiments across processes and then ...
    2. ... for each model/experiment distribute the counterfactual search across processes.
- Out-of-memory issues, data races, ...
- When using multi-processing for models and multi-threading for counterfactual search, I get low CPU efficiency on DelftBlue (jobs get cancelled).

@@

$$

$$

>>>>

- Trying to distribute: 
    1. Models/experiments across processes and then ...
    2. ... for each model/experiment distribute the counterfactual search across processes.
- Out-of-memory issues, data races, ...
- Multi-processing for models & multi-threading for counterfactual search: low CPU efficiency on DelftBlue (jobs get cancelled).

@@

Combine ideas from Energy-Based Models and Adversarial Training:

$$
\ell_{\text{clf}}(f(x),y) + \lambda_{\text{adv}} \ell_{\text{clf}}(f(x^\prime),y) + \lambda_{\text{gen}} \ell_{\text{gen}}(x^\prime,x) + \text{reg}
$$
